\textbf{How to measure maximally precise radial velocities from a set of spectra:\\ The time-independent spectrum case}

### 2019-06-11 paper/paper.tex
intro

% Style notes
% - Re-define acronyms in each section? So less flippy flippy?

@@

% text macros
\newcommand{\documentname}{\textsl{Article}}
\newcommand{\sectionname}{Section}
\newcommand{\todo}[1]{\textcolor{red}{#1}}  % gotta have \usepackage{xcolor} in main doc or this won't work
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\foreign}[1]{\textsl{#1}}
\newcommand{\HARPS}{\project{\acronym{HARPS}}}
\newcommand{\HIRES}{\project{\acronym{HIRES}}}
\newcommand{\RV}{\acronym{RV}}
\newcommand{\CRLB}{\acronym{CRLB}}

@@

\todo{needs reduction in scope, perhaps?}

Accurate spectroscopic measurements of radial velocities (\RV s) have long been a critical tool across many subfields of astronomy, from Galactic dynamics to large-scale structure and cosmic expansion.
Fundamentally, accuracy of radial-velocity mesurement is limited by the quality of spectral models of stars, or templates.
In recent decades, however, a new focus has emerged on \emph{extremely precise} but purely \emph{relative} \RV\ measurements of stars as a means of detecting exoplanets and other kinds of companions.
For this application, measuring the absolute velocity of the star is much less important than resolving changes through time.
With sub-$\mps$-level precision required for the detection of Earth-like planets, vast amounts of effort have been poured into the engineering challenges of constructing a sufficiently stable spectrograph (or, failing that, being able to track the drift of a spectrograph over time) \todo{(cite some review papers)}. At the same time, great strides have been made towards disentangling true Doppler shifts from imitative signals like the spectral signatures of stellar pulsations and magnetic activity features \todo{(cite some review papers)}.  In this work, we investigate another fundamentally important but less commonly discussed aspect of the quest for maximum-precision \RV s: the method of analysis used to estimate the \RV\ given an extracted stellar spectrum.

>>>>

% Style notes
% -----------
% - Re-define acronyms in each section? So less flippy flippy? Yes that's the thing.?
% -

% To-do items
% -----------
% - search for all \todo
% - search for all HOGG
% - search for all BEDELL
% - search for all CITE
% - should we fun-cite some ancient papers in the first paragraph, like Hubble and Oort?

@@

% text macros
\newcommand{\documentname}{\textsl{Article}}
\newcommand{\sectionname}{Section}
\newcommand{\todo}[1]{\textcolor{red}{#1}}  % gotta have \usepackage{xcolor} in main doc or this won't work
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\HARPS}{\project{\acronym{HARPS}}}
\newcommand{\HIRES}{\project{\acronym{HIRES}}}
\newcommand{\RV}{\acronym{RV}}
\newcommand{\CRLB}{\acronym{CRLB}}
\newcommand{\foreign}[1]{\textsl{#1}}

@@

It is ridiculous to open this \documentname\ by pointing out that
the spectroscopic measurement of radial velocity (\RV) has been a
critical tool across many subfields of astronomy, from Galactic
dynamics to large-scale structure and cosmic expansion.
Fundamentally, the accuracy of radial-velocity mesurement is limited
by the quality of the spectral models of the targets of the
spectroscopy.
In recent decades, however, a new focus has emerged on \emph{extremely
  precise} but \emph{purely relative} \RV\ measurements of stars as a
means of detecting exoplanets and other kinds of companions.
That is, we are looking for \emph{precision, not accuracy}.
For this application, measuring the absolute velocity of the star is
much less important than resolving changes through time.
This is the problem we address in this \documentname.

Earth-like planets induce $0.1\,\mps$-level signals in their host
stars!
Substantial hardware, software, and systems-engineering effort has
been put into the challenges of making measurements at this level of
precision (CITE some reviews).
It appears that contemporary spectrographs are stable at the
$0.05\,\mps$ level (CITE THINGS), and that the information content in
the data---which is set by the spectral features, the spectrograph
resolution, the wavelength range, and the observational
signal-to-noise (CITE THINGS)---is sufficient.
And yet, the best published \RV\ data sets show empirical scatter
(rms variations around best-fit kinematic models, for example) at the
$1\,\mps$ level (for example, CITE THINGS).
One of the motivating questions for this work is: Is it possible that
the data-analysis methodologies in use are contributing to this
empirical variance?
This is a question in information theory and inference.

\todo{syntactical reference}
